FEM Model Analysis

### 2020-12-09 FEM_R/model_analysis.Rmd
Tweaks to smkint model, still WIP

  res <- reactable(t,
            defaultColDef = colDef(
              header = function(value) gsub('_', ' ', value, fixed=TRUE),
              cell = function(value) format(value, nsmall = 2),
              align = 'center'
            ),
            columns = list(
              Variable = colDef(
                  minWidth = 160,
                  style = stickyStyle,
                  headerStyle = stickyStyle),
              P_Value_3 = pValColDef2,
              P_Value_4 = pValColDef2,
              P_Value_5 = pValColDef2,
              P_Value_6 = pValColDef2,
              P_Value_7 = pValColDef2,
              P_Value_8 = pValColDef2
            ),
            bordered = TRUE,
            highlight = TRUE,
            striped = TRUE)

@@

# Cross Validation 2 - 'Handover' plots

>>>>

  res <- reactable(t,
            defaultColDef = colDef(
              header = function(value) gsub('_', ' ', value, fixed=TRUE),
              cell = function(value) format(value, nsmall = 2),
              align = 'center'
            ),
            columns = list(
              Variable = colDef(
                  minWidth = 160,
                  style = stickyStyle,
                  headerStyle = stickyStyle),
              P_Value_1 = pValColDef2,
              P_Value_2 = pValColDef2,
              P_Value_3 = pValColDef2,
              P_Value_4 = pValColDef2,
              P_Value_5 = pValColDef2,
              P_Value_6 = pValColDef2,
              P_Value_7 = pValColDef2,
              P_Value_8 = pValColDef2
            ),
            bordered = TRUE,
            highlight = TRUE,
            striped = TRUE)

@@

# Cross Validation 2 - 'Handover' plots (Still WIP need fixing)
